---
title: "`r paste0(params$title, ': ', params$crop_name)`"
subtitle: ""
output: 
  word_document:
    reference_docx: "word-template.docx"
    toc: false
params:
  crop: NULL
  language: NULL
  traits: NULL
  collection_moments: NULL
  text: NULL
  title: NULL
  crop_name: NULL
  taxa: NULL
  autority: NULL
  authors: NULL
  centers: NULL
  survey: NULL
  version: NULL
  other_resources: NULL
---

```{r setup, include=FALSE}
library("knitr")
library("dplyr")
library("stringr")

opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

text = params$text
names(text) = c("section", "value")

get_text = function(section_id) {
  x = text$value[text$section == section_id]
  x = x[!is.na(x)]
  paste(x, collapse = "\n\n")
}
```

**Version:** `r params$version`    
**Crop:** `r params$crop_name`    
**Taxa:** *`r params$taxa`* `r params$autority`    
**Authors:** `r params$authors`    
**Institutions:** `r params$centers`     
**Traits:** `r paste(params$traits, collapse = ", ")`     
**Data collection moments:** `r paste(params$collection_moments, collapse = ", ")`     

\pagebreak

# `r get_text("intro-heading")`

```{r intro, results='asis'}
cat(get_text("intro"))
```

# `r get_text("scope-heading")`

```{r scope, results='asis'}
cat(get_text("scope"))
```

# `r get_text("consent-heading")`

```{r consent, results='asis'}
cat(get_text("consent"))
```

# `r get_text("design-heading")`

```{r design, results='asis'}
cat(get_text("design"))
```

# `r get_text("materials-heading")`

```{r materials, results='asis'}
cat(get_text("materials"))
```

# `r get_text("trial-observation-heading")`

```{r trial-observation, results='asis'}
cat(get_text("trial-observation"))
```

# `r get_text("registration-heading")`

```{r registration, results='asis'}
cat(get_text("registration"))
```

# `r get_text("socioeconomic-heading")`

```{r socioeconomic, results='asis'}
cat(get_text("socioeconomic"))
```

# `r get_text("survey-heading")`

```{r survey-intro, results='asis'}
cat(get_text("survey"))
```

```{r survey-tables, results='asis'}
for (form_name in names(params$survey)) {

  cat("\n\n## ", form_name, "\n\n", sep = "")

  tab = params$survey[[form_name]] |>
    select(`Question name` = question_name,
           `Question description` = question_desc)

  rownames(tab) = NULL

  print(knitr::kable(tab, 
                     format = "pipe"))

  cat("\n\n")
}
```

\pagebreak

# `r get_text("other-heading")`

```{r other-intro, results='asis'}
cat(get_text("other"))
```

```{r other-resources, results='asis'}
resources = params$other_resources |>
  mutate(Resource = text,
         Link = ifelse(is.na(link) | link == "", "TBD", link)) |>
  select(Resource, Link) |>
  tibble::as_tibble()

print(knitr::kable(resources, format = "pipe"))
```


